\Large Bayes network classifiers for fRMI

### 2012-09-14 proposal/proposal.tex
added bib file, planning
updated application

The dataset contains data on 6 test subjects that each completed a number of trials. For each trial (cf. Section~\ref{sec:setup}), 54 fMRI snapshots were made of specific regions of their brain. Each snapshot consists of a list of 3d pixels (so called voxels). The dimensions of these snapshots are 64x64x8 voxels, amounting to a total of 5700 voxels per snapshot (this is less than 64 * 64 * 8 because only specific regions were recorded).

Along with each snapshot, metadata is available on the state of the trial (e.g. what stimulus was active?) and what user the snapshot belongs to. For each entire trial, we also have data on the trial specifics and the result of the trial.

>>>>

The dataset contains data on 6 subjects that each completed a number of trials. For each trial (see section \ref{sec:setup}), a brain scan was made every 500 ms, totalling to approximately 54 scans per trial. Each snapshot consists of a list of approximately 5000 voxels (three dimensional pixels), of predefined regions of the brain.

Along with each snapshot, metadata is available on the state of the trial (e.g. what stimulus was shown) and what user the snapshot belongs to. For each entire trial, we also have data on the trial specifics and the result of the trial.
